Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-11 Ben_Manuscripts/structure_paper/supporting_information.tex
Edits and figure updates

  \begin{figure}
	\centering
        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
	\caption{The groups used for $g(z)$ calculations. Red atoms are in the
		tails group. Green atoms are in the head group region. The blue atom is sodium. 
		}\label{fig:monomer_color_coded}
  \end{figure}

@@

>>>>

  \begin{figure}
	\centering
        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
	\caption{The groups used for radial distribution calculations. Red atoms are in the
		tails group. Green atoms are in the head group region. The blue atom is sodium. 
		}\label{fig:monomer_color_coded}
  \end{figure}

@@

% BJC5 : Move this figure to supporting
  \begin{figure}
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disorderd Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}
